PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed age categories and sum_scores matrix -> numeric

## Categorise age into groups 
In RAMP, age is indicated categorically: 16-18, 19-25, 26-35, 36-45, 46-55, 56-65, 66-70, 71-75, 76-80, 81-85, 86-90, 91-100, 100+
Age categories in GLAD, EDGI and NBR have been created to reflect this
```{r Age groups}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
# Create categorical age groups per 10 years
dem.raw.id <- dem.raw.id %>%
  mutate(
    age_category_numeric =
      case_when(
          Age >= 16 & Age <= 18 ~ "1",
          Age >= 19 & Age <= 25 ~ "2",
          Age >= 26 & Age <= 35 ~ "3",
          Age >= 36 & Age <= 45 ~ "4",
          Age >= 46 & Age <= 55 ~ "5",
          Age >= 56 & Age <= 65 ~ "6",
          Age >= 66 & Age <= 70 ~ "7",
          Age >= 71 & Age <= 75 ~ "8",
          Age >= 76 & Age <= 80 ~ "9",
          Age >= 81 & Age <= 85 ~ "10",
          Age >= 86 & Age <= 90 ~ "11",
          Age >= 91 & Age <= 100 ~ "12",
          Age >= 101 & Age <= 120 ~ "13" # oldest person in the world is 117 years
                )
      )

@@

## Highest education (baseline, GLAD, EDGI, NBR)
Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
Assumes University degree > A level > NVQ > GCSE/O Level/CSE
```{r Highest education baseline}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
#create numeric version of the highest education variable
employment.raw.id <- employment.raw.id %>%
  mutate(
    highest_education_numeric =
      case_when(
        employment.phd_numeric == "1" ~ 4,
        employment.masters_degree_or_equivalent_numeric == "1" ~ 4,
        employment.postgraduate_degree_or_equivalent_numeric == "1" ~ 4,
        employment.bachelors_degree_or_equivalent_numeric == "1" ~ 4,
        employment.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
        employment.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
        employment.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
        employment.cses_or_equivalent_numeric == "1" ~ 1
      )
    )

@@

Check highest education coding
```{r Highest education check}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
employment.raw.id %>%
  select(highest_education,
         employment.phd_numeric,
         employment.masters_degree_or_equivalent_numeric,
         employment.postgraduate_degree_or_equivalent_numeric,
         employment.bachelors_degree_or_equivalent_numeric,
         employment.a_levelsas_levels_or_equivalent_numeric,
         employment.nvq_or_hnd_or_hnc_or_equivalent_numeric,
         employment.o_levelsgcses_or_equivalent_numeric,
         employment.cses_or_equivalent_numeric
  )
}
```

## Highest education (baseline, RAMP)
```{r highest level of education for ramp}
if(RAMP == TRUE) {
#create numeric version of the highest education variable
employment.raw.id <- employment.raw.id %>%
  mutate(
    highest_education_numeric =
      case_when(
        employment.what_is_your_highest_level_of_education == "PhD" ~ 4,
        employment.what_is_your_highest_level_of_education == "Postgraduate degree or equivalent" ~ 4,
        employment.what_is_your_highest_level_of_education == "Master's degree or equivalent" ~ 4,
        employment.what_is_your_highest_level_of_education == "Bachelor's degree or equivalent" ~ 4,
        employment.what_is_your_highest_level_of_education == "A-level or equivalent" ~ 3,
        employment.what_is_your_highest_level_of_education == "GCSE or equivalent" ~ 2,
        employment.what_is_your_highest_level_of_education == "None of these" ~ 1
      )
    )

#recode the numeric version into a factor
employment.raw.id <- employment.raw.id %>%
  mutate(
    highest_education =
      recode_factor(
        highest_education_numeric,
        `1` = "None",
        `2` = "GCSE/CSE",
        `3` = "A-levels",
        `4` = "University")
    )

Check highest education coding for RAMP
```{r Highest education check for RAMP}
if(RAMP == TRUE) {
employment.raw.id %>%
  select(highest_education,
         employment.what_is_your_highest_level_of_education,
         employment.what_is_your_highest_level_of_education_numeric
  )
}
```

@@

edgi.mhd.raw.id <- edgi.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

## RAMP
```{r ramp mhd cols}
if(RAMP == TRUE) {
ramp.mhd.raw <- readRDS(file = paste0(data.raw_path,"/ramp/mhd_ramp.rds"))
dim(ramp.mhd.raw)
colnames(ramp.mhd.raw)
}
```

```{r ramp mhd cleaning}
if(RAMP == TRUE) {
exclude_cols <- c("Sample",
                  "ID")

ramp.mhd.raw.id <- ramp.mhd.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  separate(ID, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    mhd.depression = NA.30.depression,
    mhd.pregnancy_depression = NA.30.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = NA.30.premenstrual_dysphoric_disorder_pmdd,
    mhd.mania_hypomania_bipolar_or_manicdepression = NA.30.mania_hypomania_bipolar_or_manicdepression,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = NA.30.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = NA.30.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = NA.30.specific_phobia_e.g._phobia_of_flying,
    mhd.agoraphobia = NA.30.agoraphobia,
    mhd.panic_disorder = NA.30.panic_disorder,
    mhd.panic_attacks = NA.30.panic_attacks,
    mhd.posttraumatic_stress_disorder_ptsd = NA.30.posttraumatic_stress_disorder_ptsd,
    mhd.obsessivecompulsive_disorder_ocd = NA.30.obsessivecompulsive_disorder_ocd, 
    mhd.body_dysmorphic_disorder_bdd = NA.30.body_dysmorphic_disorder_bdd,
    mhd.skin_picking_obsessive_compulsive = NA.30.skin_picking_obsessive_compulsive,
    mhd.anorexia_nervosa = NA.30.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa = NA.30.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa = NA.30.bulimia_nervosa,
    mhd.bingeeating_disorder = NA.30.psychological_overeating_or_bingeeating_disorder,
    mhd.schizophrenia = NA.30.schizophrenia,
    mhd.schizoaffective_disorder = NA.30.schizoaffective_disorder,
    mhd.type_psychosis_psychotic_illness = NA.30.psychosis_type_psychotic_illness,
    mhd.personality_disorder = NA.30.personality_disorder,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = NA.30.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder = NA.30.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_diagnosed = NA.30.personality_disorder_diagnosed
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(ramp.mhd.raw.id)
# Inspect colnames
colnames(ramp.mhd.raw.id)
#Differences
dim(ramp.mhd.raw)[1]-dim(ramp.mhd.raw.id)[1]
}
```

```{r ramp mhd copy}
if(RAMP == TRUE) {
  mhd.raw.id <- ramp.mhd.raw.id
}
```

@@

```{r Check eating_disorders}
if(EDGI == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.bingeeating_disorder_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder
  )
}
```

### Obsessive compulsive disorders
```{r mhd obsessive_compulsive_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhd.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhd.obsessive_compulsive_related_disorders_numeric == "0" &
        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

@@

```{r mhd obsessive_compulsive_disorders for ramp}
if(RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhd.skin_picking_obsessive_compulsive_numeric == "1" ~ 1,
        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhd.skin_picking_obsessive_compulsive_numeric == "0" &
        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

```{r Check obsessive_compulsive_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
mhd.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhd.obsessivecompulsive_disorder_ocd,
    mhd.obsessivecompulsive_disorder_ocd_numeric,
    mhd.obsessive_compulsive_related_disorders,
    mhd.obsessive_compulsive_related_disorders_numeric,
    mhd.body_dysmorphic_disorder_bdd,
    mhd.body_dysmorphic_disorder_bdd_numeric
  )
}
```

```{r Check obsessive_compulsive_disorders ramp}
if(RAMP == TRUE) {
mhd.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhd.obsessivecompulsive_disorder_ocd,
    mhd.obsessivecompulsive_disorder_ocd_numeric,
    mhd.skin_picking_obsessive_compulsive,
    mhd.skin_picking_obsessive_compulsive_numeric,
    mhd.body_dysmorphic_disorder_bdd,
    mhd.body_dysmorphic_disorder_bdd_numeric
  )
}
```

@@

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    comorbidity_total_count_factor =
      recode_factor(comorbidity_total_count_factor_numeric,
                    "0" = "No comorbidity",
                    "1" = "1 comorbid disoder",
                    "2" = "2 comorbid disoders",
                    "3" = "3+ comorbid disoder",
                    missing = NA_character_
                    )
  )

@@

Create new dataframe with the derived categories
```{r mhd categories}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
    personality_cluster_a_numeric,
    personality_cluster_a,
    personality_cluster_b_numeric,
    personality_cluster_b,
    personality_cluster_c_numeric,
    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    )
}
```

```{r mhd categories}
if(EDGI == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
#    personality_cluster_a_numeric,
#    personality_cluster_a,
#    personality_cluster_b_numeric,
#    personality_cluster_b,
#    personality_cluster_c_numeric,
#    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    ) %>%
  add_column(
    personality_cluster_a_numeric = NA_real_,
    personality_cluster_a = NA_real_,
    personality_cluster_b_numeric = NA_real_,
    personality_cluster_b = NA_real_,
    personality_cluster_c_numeric = NA_real_,
    personality_cluster_c = NA_real_    
  )
}
```

@@

# Calulate total score
gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
                                        items = prepan.gad.raw.id[gad.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
prepan.gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores

@@

# Calulate total score
pcl.scored_items_prepan <- scoreItems(keys = pcl.items_key_prepan,
                                        items = prepan.pcl.raw.id[pcl.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 1, 
                                        max = 5)
# Add in column to tibble
prepan.pcl.raw.id$pcl.sum_score_prepan_raw <- pcl.scored_items_prepan$scores

@@

# Calulate sum score
phq.scored_items_prepan <- scoreItems(keys = phq.items_key_prepan,
                                        items = prepan.phq.raw.id[phq.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
prepan.phq.raw.id$phq.sum_score_prepan_raw <- phq.scored_items_prepan$scores

@@

## RAMP
```{r coping ramp gad cols}
if(RAMP == TRUE) {
  ramp.gad.raw <- readRDS(file = paste0(data.raw_path,"/ramp/gad_ramp.rds"))
  dim(ramp.gad.raw)
  colnames(ramp.gad.raw)
}
```

```{r coping ramp gad summary}
if(RAMP == TRUE) {
  summarytools::dfSummary(
    ramp.gad.raw,
    graph.col = F,
    valid.col = F,
    labels.col = F
  )
}
```

```{r coping ramp gad cleaning}
if(RAMP == TRUE) {
  exclude_cols_ramp <- c(
    "Sample",
    "ID",
    "startDate.ramp"
  )

>>>>

## Categorise age into groups 
In RAMP, age is indicated categorically: 16-18, 19-25, 26-35, 36-45, 46-55, 56-65, 66-70, 71-75, 76-80, 81-85, 86-90, 91-100, 100+
Age categories in GLAD, EDGI and NBR have been created to reflect this
```{r Age groups}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
# Create categorical age groups per 10 years
dem.raw.id <- dem.raw.id %>%
  mutate(
    age_category_numeric =
      case_when(
          Age >= 16 & Age <= 18 ~ 1,
          Age >= 19 & Age <= 25 ~ 2,
          Age >= 26 & Age <= 35 ~ 3,
          Age >= 36 & Age <= 45 ~ 4,
          Age >= 46 & Age <= 55 ~ 5,
          Age >= 56 & Age <= 65 ~ 6,
          Age >= 66 & Age <= 70 ~ 7,
          Age >= 71 & Age <= 75 ~ 8,
          Age >= 76 & Age <= 80 ~ 9,
          Age >= 81 & Age <= 85 ~ 10,
          Age >= 86 & Age <= 90 ~ 11,
          Age >= 91 & Age <= 100 ~ 12,
          Age >= 101 & Age <= 120 ~ 13 # oldest person in the world is 117 years
                )
      )

@@

## Highest education (baseline, GLAD, EDGI, NBR, RAMP)
Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
Assumes University degree > A level > NVQ > GCSE/O Level/CSE
```{r Highest education baseline}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
#create numeric version of the highest education variable
employment.raw.id <- employment.raw.id %>%
  mutate(
    highest_education_numeric =
      case_when(
        employment.phd_numeric == "1" ~ 4,
        employment.masters_degree_or_equivalent_numeric == "1" ~ 4,
        employment.postgraduate_degree_or_equivalent_numeric == "1" ~ 4,
        employment.bachelors_degree_or_equivalent_numeric == "1" ~ 4,
        employment.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
        employment.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
        employment.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
        employment.cses_or_equivalent_numeric == "1" ~ 1
      )
    )

@@

Check highest education coding
```{r Highest education check}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
employment.raw.id %>%
  select(highest_education,
         employment.phd_numeric,
         employment.masters_degree_or_equivalent_numeric,
         employment.postgraduate_degree_or_equivalent_numeric,
         employment.bachelors_degree_or_equivalent_numeric,
         employment.a_levelsas_levels_or_equivalent_numeric,
         employment.nvq_or_hnd_or_hnc_or_equivalent_numeric,
         employment.o_levelsgcses_or_equivalent_numeric,
         employment.cses_or_equivalent_numeric
  )
}
```

@@

edgi.mhd.raw.id <- edgi.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder,
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

@@

```{r Check eating_disorders}
if(EDGI == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.bingeeating_disorder_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder,
  )
}
```

### Obsessive compulsive disorders
```{r mhd obsessive_compulsive_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhd.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhd.obsessive_compulsive_related_disorders_numeric == "0" &
        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

@@

```{r Check obsessive_compulsive_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhd.obsessivecompulsive_disorder_ocd,
    mhd.obsessivecompulsive_disorder_ocd_numeric,
    mhd.obsessive_compulsive_related_disorders,
    mhd.obsessive_compulsive_related_disorders_numeric,
    mhd.body_dysmorphic_disorder_bdd,
    mhd.body_dysmorphic_disorder_bdd_numeric
  )
}
```

@@

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    comorbidity_total_count_factor =
      recode_factor(comorbidity_total_count_factor_numeric,
                    "0" = "No comorbidity",
                    "1" = "1 comorbid disoder",
                    "2" = "2 comorbid disoders",
                    "3" = "3+ comorbid disoders",
                    missing = NA_character_
                    )
  )

@@

Create new dataframe with the derived categories
++KT: do we want to keep individual diagnoses here as well?? 
```{r mhd categories}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
    personality_cluster_a_numeric,
    personality_cluster_a,
    personality_cluster_b_numeric,
    personality_cluster_b,
    personality_cluster_c_numeric,
    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    )
}
```

```{r mhd categories}
if(EDGI == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
#    personality_cluster_a_numeric,
#    personality_cluster_a,
#    personality_cluster_b_numeric,
#    personality_cluster_b,
#    personality_cluster_c_numeric,
#    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    ) %>%
  add_column(
    personality_cluster_a_numeric = NA_real_,
    personality_cluster_a = NA_real_,
    personality_cluster_b_numeric = NA_real_,
    personality_cluster_b = NA_real_,
    personality_cluster_c_numeric = NA_real_,
    personality_cluster_c = NA_real_,    
  )
}
```

@@

# Calulate total score
gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
                                        items = prepan.gad.raw.id[gad.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
prepan.gad.raw.id$gad.sum_score_prepan_raw <- as.numeric(gad.scored_items_prepan$scores)

@@

# Calulate total score
pcl.scored_items_prepan <- scoreItems(keys = pcl.items_key_prepan,
                                        items = prepan.pcl.raw.id[pcl.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 1, 
                                        max = 5)
# Add in column to tibble
prepan.pcl.raw.id$pcl.sum_score_prepan_raw <- as.numeric(pcl.scored_items_prepan$scores)

@@

# Calulate sum score
phq.scored_items_prepan <- scoreItems(keys = phq.items_key_prepan,
                                        items = prepan.phq.raw.id[phq.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
prepan.phq.raw.id$phq.sum_score_prepan_raw <- as.numeric(phq.scored_items_prepan$scores)

@@

## RAMP
```{r coping ramp gad cols}
if(RAMP == TRUE) {
  coping.ramp.gad.raw <- readRDS(file = paste0(data.raw_path,"/ramp/gad_coping_ramp.rds"))
  dim(coping.ramp.gad.raw)
  colnames(coping.ramp.gad.raw)
}
```

```{r coping ramp gad summary}
if(RAMP == TRUE) {
  summarytools::dfSummary(
    coping.ramp.gad.raw,
    graph.col = F,
    valid.col = F,
    labels.col = F
  )
}
```

```{r coping ramp gad cleaning}
if(RAMP == TRUE) {
  exclude_cols_coping_ramp <- c(
    "Sample",
    "ID",
    "startDate.coping"
  )
